\pdftitle

### 2017-05-16 maxNt.tex
fix green todos

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-15T22:57:55+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\begin{abstract}
  ***%  The abstract must be limited to one paragraph.
\end{abstract}

%\section{Implicit assumptions in the maximum-entropy method}
\section{Introduction}

Recent advances in electrophysiological techniques allow to
record from large population of neurons [\cite]. The recorded neurons
are usually picked out from a specific area according to an unknown process, and from their
observation in relation to stimuli or behavioral task, we strive for
understanding the mechanism behind neuronal coding. That is, they are assumed to be a
\enquote{representative random sample} of the neurons in that area.

Huge amount of parallel recordings from hundreds of neurons,
available today, is accompanied by the statistical challenges
to be employed for shedding light on the mechanism behind neuronal coding. 
The principle of \me\ was proposed as a way to overcome these challenges by
constructing a full description of the 
neuronal firing patterns. The \me\ method employs only first and second
order statistics of the representative random sample to construct 
a \enquote{maximally noncommittal} \cite{jaynes1963} 
probability distribution of the firing patterns [\cite].

Using the pairwise \me\ models many studies investigated the
 questions such as, which level of interaction (pairwise or higher-order) between neurons
 is suffiecient to explain the observed experimental data [\cite]? Or how collective behavior
 of neurons can be related to stimuli or behavioral tasks [\cite]? add more **

Here we show that there is a
contradiction in applying \me\ to the representative random sample
of neurons to generate a maximally noncommital distribution for
that sample.

@@

Suppose our desired constraints are $\expe{\yxs } = c_1$ and
$\expe{\yxxs} = c_2$, the expectations being given by the fourth term of
\eqn~\eqref{eq:expe_products}. Applying \me\ to the distribution of the
average of the full population we find
\begin{equation}
  \label{eq:full_pop_av_example_ME}
  \p(\yXf = \yRf \| \yHa)  = \yL\,
\binom{N}{N \yRf}\exp\biggl[
\yL_2\, \frac{\yRf\,(N \yRf-1)}{N-1} + \yL_1\, \yRf\biggr]
\end{equation}
with such parameters $\yL$, $\yL_1$, $\yL_2$ as to satisfy normalization
and constraints. We call this state of knowledge $\yHa$. Marginalization by
\eqn~\eqref{eq:marginal} then gives
\begin{equation}
  \label{eq:full_pop_av_example_ME_marg}
  \p(\yxs = \yrs \| \yHa)  = \yL
  \sum_{N\yRf=0}^N
  \binom{n}{n\yrs} \binom{N-n}{N\yRf-n\yrs} \exp\biggl[
\yL_2\, \frac{\yRf\,(N \yRf-1)}{N-1} + \yL_1\, \yRf\biggr].
\end{equation}
Applying \me\ to the distribution of the average of the sample, using the
third term of \eqn~\eqref{eq:expe_products}, we find
\begin{equation}
  \label{eq:sample_av_example_ME}
  \p(\yxs = \yrs \| \yHb)  = \yl\,
  \binom{n}{n\yrs}
  \exp\biggl[\yl_2\, \frac{\yrs\,(n \yrs-1)}{n-1} + \yl_1\, \yrs\biggr]
\end{equation}
with such parameters $\yl$, $\yl_1$, $\yl_2$ as to satisfy the constraints.
We call this state of knowledge $\yHb$.
%\setlength{\intextsep}{0.5ex}%
%\begin{wrapfigure}{r}{0.5\linewidth}
\begin{figure}[!t]
\centering
\includegraphics[width=0.99\linewidth]{different_maxent_pop_sample_100.pdf}%
\caption{Plots of $\p(\yxs = \yrs)$ constructed by \me\ at the population
  level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:full_pop_av_example_ME_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:sample_av_example_ME}. In this case $N=5\,000$,
  $n=100$, $\expe{\yxs}=0.45$, $\expe{\yxxs}=0.35$, $\yL_1 = -13\,321.9$,
  $\yL_2 = 13\,321.5$, $\yl_1=-269.3$, $\yl_2 = 268.9$.}
\label{fig:diff_maxent_pop_sample}
\end{figure}%maxent_pop_or_sample.nb
% \end{wrapfigure}
\begin{figure}[!t]
\centering
\includegraphics[width=0.99\linewidth]{different_maxent_pop_sample_200_realdata_both.pdf}
% 
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at
  the population level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:full_pop_av_example_ME_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:sample_av_example_ME}. In this case $N=5\,000$,
  $n=200$, $\expe{\yxs}=0.045$, $\expe{\yxxs}=0.0025$,
  $\yL_1 = -16\,834.0$, $\yL_2 = 16\,825.7$, $\yl_1=-673.5$,
  $\yl_2 = 665.1$.}
\label{fig:diff_maxent_pop_sample_realdata}
\end{figure}%maxent_pop_or_sample.nb

@@

PGLPM thanks Mari \amp\ Miri for continuous encouragement and affection,
Buster Keaton for filling life with awe and inspiration, and the developers
and maintainers of \LaTeX, Emacs, AUC\TeX, MiK\TeX, arXiv, biorXiv,
PhilSci, Hal archives, Python, Inkscape, Sci-Hub for making a free and
unfiltered scientific exchange possible.

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2017-05-16T01:37:28+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

\begin{abstract}
  \mynote{Better title?}
  ***%  The abstract must be limited to one paragraph.
\end{abstract}

\section{Implicit assumptions in the maximum-entropy method}

The \me\ method is used in neuroscience blahblah***

@@

Suppose our desired constraints are $\expe{\yxs } = c_1$ and
$\expe{\yxxs} = c_2$, the expectations being given by the fourth term of
\eqn~\eqref{eq:expe_products}. Applying \me\ to the distribution of the
average of the full population we find
\begin{equation}
  \label{eq:full_pop_av_example_ME}
  \p(\yXf = \yRf \| \yHa)  = \yL\,
\binom{N}{N \yRf}\exp\biggl[
\yL_2 \yRf \,\frac{N \yRf-1}{N-1} + \yL_1\, \yRf\biggr]
\end{equation}
with such parameters $\yL$, $\yL_1$, $\yL_2$ as to satisfy normalization
and constraints. We call this state of knowledge $\yHa$. Marginalization by
\eqn~\eqref{eq:marginal} then gives
\begin{equation}
  \label{eq:full_pop_av_example_ME_marg}
  \p(\yxs = \yrs \| \yHa)  = \yL
  \sum_{N\yRf=0}^N
  \binom{n}{n\yrs} \binom{N-n}{N\yRf-n\yrs} \exp\biggl[
\yL_2 \yRf \,\frac{N \yRf-1}{N-1} + \yL_1\, \yRf\biggr].
\end{equation}
Applying \me\ to the distribution of the average of the sample, using the
third term of \eqn~\eqref{eq:expe_products}, we find
\begin{equation}
  \label{eq:sample_av_example_ME}
  \p(\yxs = \yrs \| \yHb)  = \yl\,
  \binom{n}{n\yrs}
  \exp\biggl[\yl_2 \yrs \,\frac{n \yrs-1}{n-1} + \yl_1\, \yrs\biggr]
\end{equation}
with such parameters $\yl$, $\yl_1$, $\yl_2$ as to satisfy the constraints.
We call this state of knowledge $\yHb$.
%\setlength{\intextsep}{0.5ex}%
%\begin{wrapfigure}{r}{0.5\linewidth}
\begin{figure}[!t]
\centering
\includegraphics[width=0.99\linewidth]{different_maxent_pop_sample_100.pdf}%
\caption{Plots of $\p(\yxs = \yrs)$ constructed by \me\ at the population
  level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:full_pop_av_example_ME_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:sample_av_example_ME}. In this case $N=5\,000$,
  $n=100$, $\expe{\yxs}=0.45$, $\expe{\yxxs}=0.35$, $\yL_1 = -13\,321.9$,
  $\yL_2 = 13\,321.5$, $\yl_1=-269.3$, $\yl_2 = 268.9$.}
\label{fig:diff_maxent_pop_sample}
\end{figure}%maxent_pop_or_sample.nb
% \end{wrapfigure}
\begin{figure}[!t]
\centering
\includegraphics[width=0.99\linewidth]{different_maxent_pop_sample_200_realdata_both.pdf}
% 
\caption{Linear and log-plots of $\p(\yxs = \yrs)$ constructed by \me\ at
  the population level followed by sample marginalization (blue triangles),
  \eqn~\eqref{eq:full_pop_av_example_ME_marg}, and at the sample level (red
  circles), \eqn~\eqref{eq:sample_av_example_ME}. In this case $N=5\,000$,
  $n=200$, $\expe{\yxs}=0.045$, $\expe{\yxxs}=0.0025$,
  $\yL_1 = -16\,834.0$, $\yL_2 = 16\,825.7$, $\yl_1=-673.5$,
  $\yl_2 = 665.1$.}
\label{fig:diff_maxent_pop_sample_realdata}
\end{figure}%maxent_pop_or_sample.nb

@@

To be added after review.
\iffalse PGLPM thanks Mari \amp\ Miri for continuous encouragement and affection,
Buster Keaton for filling life with awe and inspiration, and the developers
and maintainers of \LaTeX, Emacs, AUC\TeX, MiK\TeX, arXiv, biorXiv,
PhilSci, Hal archives, Python, Inkscape, Sci-Hub for making a free and
unfiltered scientific exchange possible.\fi
